---
title: "Introduction of R Packages"
author: "®yo, Eng Lian Hu"
date: "8/28/2015"
output:
  html_document:
    fig_height: 3
    fig_width: 5
    highlight: haddock
    theme: cerulean
    toc: yes
---

# 1. Introduction

  This is an casting page of testing the efficiency of the coding and also some useful r packages for the research on `Betting Strategy and Model Validation`. Some packages are introduce from other websites while I made it a scrapbook to easier for references.

```{r libs}
## Setup Options, Loading Required Libraries and Preparing Environment
## Loading the packages and setting adjustment
suppressMessages(library('BBmisc'))
suppressAll(library('utils'))
suppressAll(source('./function/libs.R', local = TRUE))
```

```{r read-data1}
## Load saved dataset to save the loading time.
## directly load the dataset from running chunk `read-data-summary-table` and also chunk `scrap-data`. 
## The spboData for filtering leagues and matches scores purpose. Kindly refer to file named 
## `compacted data - shinyData.txt` inside folder `data`.

## Run above codes and save.images() and now directly load for shinyApp use.
load('./regressionApps/shinyData.RData', envir = .GlobalEnv)

## -------- chunk `bank-roll` -----------
## Re-categorise the soccer financial settlement date. Due to I have no the history matches dataset from bookmakers. The scrapped spbo time is not stable (always change, moreover there just an information website) where firm A is the firm who placed bets with millions HKD (although the kick-off time might also changed after placed that particular bet), therefore I follow the kick-off time of the firm A.
#'@ dat <- dat[order(dat$DateUK),] %>% mutate(DateUS = as.Date(format(DateUK, tz = 'EST', usetz = TRUE, format = '%Y-%m-%d %H:%M:%S'))) #daily settlement will base on variable `DateUS`.
```

# 2. R Packages

## 2.1 Read Files

  In my previous assignments, there has some useful function for read files :
  
  - `scan()` - scan the table files.
  - `readLines()` - read the files line by line.
  - `readtable()` - read the table files.
  - `readBin()` - fatest since read the binary code and convert to character.

  - [Coursera Data Science Capstone](https://github.com/englianhu/Coursera-Data-Science-Capstone)
  - [Coursera Data Mining](https://github.com/englianhu/Coursera-Data-Mining)

  Below is codes for merge files, there has another function which is `plyr::join_all()` which is very efficient, however the datetime format will became 0 value but `reshape::merge_all()` can combine the data efficiently but taken longer time.

```{r get-data-summary-table-2.1, warning = FALSE}
nrow(do.call(rbind, llply(as.list(seq(2011, 2015)), function(x) data.frame(Sess = x, read.csv(paste0('./data/', x, '.csv'))), .parallel = TRUE)))

nrow(bind_rows(llply(as.list(seq(2011, 2015)), function(x) data.frame(Sess = x, read.csv(paste0('./data/', x, '.csv'))), .parallel = TRUE)))

system.time(do.call(rbind, llply(as.list(seq(2011,2015)), function(x) data.frame(Sess = x, read.csv(paste0('./data/', x, '.csv'))), .parallel = TRUE)))

system.time(bind_rows(llply(as.list(seq(2011, 2015)), function(x) data.frame(Sess = x, read.csv(paste0('./data/', x, '.csv'))), .parallel = TRUE)))

system.time(bind_rows(llply(as.list(seq(2011, 2015)), function(x) data.frame(Sess = x, data.table::fread(paste0('./data/', x, '.csv'))), .parallel = TRUE)))
```

  You can also embed plots, for example:

```{r merge_all-dataframes-2.2}
#'@ system.time(Reduce(function(x,y) {merge(x,y,all=TRUE)}, llply(list(df1,df1.sps,df1.pst),function(x) x[[1]])))

#'@ system.time(merge_all(list(df1[[1]],df1.sps[[1]],df1.pst[[1]])))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
#'@ system.time(merge(socData, othData, all=TRUE))

#'@ system.time(merge_all(list(socData, othData)))
```

## 2.2 html Format Table

  There are quite some r packages for ploting html table :


```{r html-table}
suppressMessages(library('knitr'))
suppressMessages(library('xtable'))
suppressMessages(library('htmlTable'))
suppressMessages(library('plyr'))
suppressMessages(library('dplyr'))
suppressMessages(library('formattable'))

## Re-categorise the soccer financial settlement date. Due to I have no the history matches dataset from bookmakers. The scrapped spbo time is not stable (always change, moreover there just an information website) where firm A is the firm who placed bets with millions HKD (although the kick-off time might also changed after placed that particular bet), therefore I follow the kick-off time of the firm A.
dat <- dat[order(dat$DateUK),] %>% mutate(DateUS = as.Date(format(DateUK, tz = 'EST', usetz = TRUE, format = '%Y-%m-%d %H:%M:%S'))) #daily settlement will base on variable `DateUS`.

BR <- ddply(dat, .(DateUS), summarise, Stakes = sum(Stakes), Return = sum(Return), PL = sum(PL), n = length(Sess), rRates = Return / Stakes) %>% mutate(CumStakes = cumsum(Stakes), SPL = cumsum(PL), BR = 4600 + SPL, gRates = BR/CumStakes)

summary(BR)
summary(BR) %>% formattable 
summary(BR) %>% formattable %>% as.htmlwidget
kable(summary(BR))
htmlTable(summary(BR))
print(xtable(summary(BR)), type = 'html')
```

## 2.3 Econometric and Investment

### 2.3.1 数据管理：

包括数据集抓取、存储、读取、时间序列、数据处理等，涉及R包

1. zoo (时间序列对象)
2. xts (时间序列处理)
3. timeSeries (Rmetrics系时间序列对象) 
4. timeDate (Rmetrics系时间序列处理)
5. data.table (数据处理)
6. quantmod (数据下载和图形可视化)
7. RQuantLib (QuantLib数据接口)
8. WindR (Wind数据接口)
9. RJDBC (数据库访问接口)
10. rhadoop (Hadoop访问接口)
11. rhive (Hive访问接口)
12. rredis (Redis访问接口)
13. rmongodb (MongoDB访问接口)
14. SparkR (Spark访问接口)
15. fImport (Rmetrics系数据访问接口)等。

### 2.3.2 指标计算：

包括金融市场的技术指标的各种计算方法，涉及R包

1. TTR (技术指标),
2. TSA (时间序列计算)
3. urca (单位根检验)
4. fArma (Rmetrics系ARMA计算)
5. fAsianOptions (Rmetrics系亚洲期权定价)
6. fBasics (Rmetrics系计算工具)
7. fCopulae (Rmetrics系财务分析)
8. fExoticOptions (Rmetrics系期权计算)
9. fGarch (Rmetrics系Garch模型)
10. fNonlinear (Rmetrics系非线模型)
11. fOptions (Rmetrics系期权定价)
12. fRegression (Rmetrics系回归分析)
13. fUnitRoots (Rmetrics系单位根检验)等。

### 2.3.3 回测交易：

包括金融数据建模，并验证用历史数据验证模型的可靠性，涉及R包

1. FinancialInstrument(金融产品),
2. quantstrat(策略模型和回测),
3. blotter(账户管理)
4. fTrading(Rmetrics系交易分析)

### 2.3.4 投资组合：

对多策略或多模型进行管理和优化，涉及R包

1. PortfolioAnalytics(组合分析和优化)
2. stockPortfolio(股票组合管理)
3. fAssets(Rmetrics系组合管理)等

### 2.3.5 风险管理：

对持仓进行风险指标的计算和风险提示，涉及R包
1. PerformanceAnalytics(风险分析)
2. fPortfolio(Rmetrics系组合优化)
3. fExtremes(Rmetrics系数据处理)

## 2.4 Time Format

1. lubridate (very easy to convert the time format or select the year, month, week, day, hour, min, scd variables, however some format unable fit to tbl_df or it became 0 value when plot a datatable graph)
2. zoo
3. ts
4. chron
5. timeDate
6. xts

  (I am moving this from the comments to the answer portion of stackoverflow at the request of the original poster.)

  There is an article in [R News 4/1](http://cran.r-project.org/doc/Rnews/Rnews_2004-1.pdf) ("R Help Desk", p. 29) that specifically compares Date, POSIXct and `chron`. (The 1st two are in core of R and `chron` is a package.)

  - `timeDate` class (in the `timeDate` package) is based on POSIXct but has extra time zone/financial center support.
  - For regularly spaced series the the `tis` package supports many notions of dates.
  - The `mondate` package supports accounting dates.
  - The `zoo` time series package supports just about any date/time class and also has `yearmon` and `yearqtr` for `ts` compatibility.
  - The `xts` time series package works on top of `zoo` and handles the most common date/time classes by translating them to `POSIXct` and back again.
  - There is also information in the [Time Series CRAN Task View](http://cran.r-project.org/web/views/TimeSeries.html).

  Reference : [Which R time/date class and package to use?](http://stackoverflow.com/questions/4354974/which-r-time-date-class-and-package-to-use)

## 2.5 Data Visualization

  In my first time ploting graph in [Betting Strategy and Model Validation](https://github.com/scibrokes/betting-strategy-and-model-validation/tree/master/data), I use `ggplot2` with some `ggplotthemes` and `directlable` etc to enhance the data visualization effects but later on I use interactive JS plot. Below r packages are useful for plot graph.
  
  - ggplot2 - one of the best static visualization packages in R
  - ggvis - interactive plots from the makers of ggplot2
  - rCharts - R interface to multiple javascript charting libraries
  - plotly - convert ggplot2 figures to interactive plots easily
  - googleVis - use Google Chart Tools from R
  - RECharts (two packages from Xie Yihui and Wei Taiyun)
  - [highcharter](http://jkunst.com/highcharter/index.html) - An interative d3 chart

```{r bank-roll1, results = 'asis'}
suppressAll(library('highcharter'))
suppressAll(source('./function/compareKelly.R'))

## Applied various fractional Kelly models version I.
##   stakes based reverser models.
if(file.exists('./data/K1D1.rds')) {
  K1D1 <- read_rds(path = './data/K1D1.rds')
} else {
  K1D1 <- vKelly(dat, type = 'D1')
}

plotFund <- compareKelly(K1D1, chart = TRUE, type = 'single')
plotFund
```

*graph 2.5.1 : Candle stick chart.*

```{r bank-roll2, results = 'asis'}
suppressAll(library('highcharter'))
suppressAll(source('./function/compareKelly.R'))

plotFund <- compareKelly(K1D1, chart = TRUE, type = 'multiple')
plotFund
```

*graph 2.5.2 : Comparison of multiple funds chart.*

```{r}
## Need to correct the content, below just a sample...

## Random pick 2 observations among each stratified levels of Result.
K <- llply(split(dat, dat$Result), function(x) x[sample(nrow(x), 2), c('Result', 'Return', 'EUPrice', 'HKPrice', 'Stakes', 'Rebates')]) %>% ldply(., .id = 'Result') %>% mutate(KReturn = currency(Return), Return = currency(Return), KStakes = currency(Stakes), Stakes = currency(Stakes), Rebates = percent(Rebates), Change = percent(KStakes / Stakes - 1)) %>% .[sample(nrow(.), nrow(.)), ]

## http://www.w3schools.com/colors/colors_picker.asp
tagList(
  tags$div(align = "center", 
           class = "bg-info", 
           tags$h3(class = "bg-primary", "Comparison of Return of Staking"), 
           tags$h5(align = "center", class = "text-muted", 
                   "Difference of PL btw Normal and Kelly Staking. (Sample)")), 
  
  as.htmlwidget(K %>% formattable(list(
    
    Result = formatter('span', style = x ~ ifelse(x == 'Win', style(color = '#269900', font.weight = 'bold'), ifelse(x == 'Half Win', style(color = '#40FF00'), ifelse(x == 'Push', style(color = '#FFFF00'), ifelse(x == 'Half Loss', style(color = '#FF8C1A'), ifelse(x == 'Loss', style(color = '#FF0000', font.weight = 'bold'), NA)))))),
    
    KReturn = formatter('span', style = ~ style(color = ifelse(KReturn >= KStakes, 'green', 'red')), ~ icontext(ifelse(KReturn >= KStakes, 'plus-sign', 'minus-sign'), KReturn)),
    
    Return = formatter('span', style = ~ style(color = ifelse(Return >= Stakes, 'green', 'red')), ~ icontext(ifelse(Return >= Stakes, 'plus-sign', 'minus-sign'), Return)),
    
    EUPrice = color_tile('white', '#003D99'),
    HKPrice = color_tile('white', '#003D99'),
    KStakes = color_tile('white', '#CC9900'),
    Stakes = color_tile('white', '#CC9900'),
    
    Change = formatter('span', style = ~ style(color = ifelse(Change < 0, 'red', 'green')), ~ icontext(ifelse(Change < 0, 'arrow-down', 'arrow-up'), Change))))))
```

*table 2.5.1 : Price flutuation table.*

Reference :
  - [Interactive visualizations with R - a minireview](http://ouzor.github.io/blog/2014/11/21/interactive-visualizations.html)
  - [Interactive DataViz with R](https://rpubs.com/asarapure/data_con)
  - [Coursera Data Mining](https://github.com/englianhu/Coursera-Data-Mining) (in my previous assignments, there are some r useful packages like `DT`, `rCharts::dTable()` and `formattable`)

  Also other libraries for creating interactive visualizations from R do exist, such as `clickme`, `RIGHT`, `ggobi`, `iplots`, `gg2v`, `rVega`, `cranvas` and `r2d3`. Some of these are not under active development anymore. I might include some of those into the comparison here in the future. The `d3Network` package is also worth checking if you need cool interactive network visualizations.

# 3. Conclusion 

  From the research, I learned from some articles which compare the efficiency of data measurement which will apply in future data analyse and data mining etc.

  - [Comparing performance of by, ddply and data.table](http://www.r-bloggers.com/transforming-subsets-of-data-in-r-with-by-ddply-and-data-table/)
  - [R高性能包介绍与并行运算](https://mp.weixin.qq.com/s?__biz=MzA3NDUxMjYzMA%3D%3D&mid=216065319&idx=1&sn=31af52816c7e8b937f15480c4d5f6e41&key=0acd51d81cb052bcbc420864d8003491eba2f4bbc722bf3a7bc7da0d59fefc64ea6fc32bdb33673eebd62f201cbc2190&ascene=7&uin=MjAwMTM4MjU0OA%3D%3D&devicetype=android-19&version=26020236&nettype=WIFI&pass_ticket=GdViEIR%2F5PLzVFnzLxc71K39ze4fb6VAwvFp1bhH3inbu5xBjyQ7BLEpDOrQhWZ1)
  - [A biased comparsion of JSON packages in R](https://rstudio-pubs-static.s3.amazonaws.com/31702_9c22e3d1a0c44968a4a1f9656f1800ab.html)
  - [Video how-to: Speed up R with C++ and Rcpp](http://www.computerworld.com/article/2961056/data-analytics/video-how-to-speed-up-r-with-c-plus-plus-and-rcpp-package.html)
  - [benchmarking logistic regression using glm.fit , bigglm, speedglm, glmnet, LiblineaR](http://stackoverflow.com/questions/19532651/benchmarking-logistic-regression-using-glm-fit-bigglm-speedglm-glmnet-libli)
  - [Dates and Times Made Easy with lubridate](http://www.jstatsoft.org/article/view/v040i03/v40i03.pdf)
  - [Tables with htmlTable and some alternatives](https://cran.r-project.org/web/packages/htmlTable/vignettes/tables.html)
  - [R语言量化投资常用包总结](http://mp.weixin.qq.com/s?__biz=MzA3MTM3NTA5Ng==&mid=2651054987&idx=1&sn=11c6bb68dbb0d77598a1d2459cff6dcf&chksm=84d9c21cb3ae4b0ade8f398760e6414be06c4e9cb69d1389df46e326fd481e3320c9ffb92319&scene=0#wechat_redirect)
  - [Do more with dates and times in R with lubridate 1.3.0](https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html)
  - [Which R time/date class and package to use?](http://stackoverflow.com/questions/4354974/which-r-time-date-class-and-package-to-use)
  - [Interactive visualizations with R - a minireview](http://ouzor.github.io/blog/2014/11/21/interactive-visualizations.html)
  - [Interactive DataViz with R](https://rpubs.com/asarapure/data_con)
  - [Coursera Data Mining](https://github.com/englianhu/Coursera-Data-Mining)
