---
title: "test2"
author: "Ryo, Eng Lian Hu"
date: "1/22/2016"
output: html_document
---

  This is an natural language analysis on the matching soccer teams' name when I am doing research on [Betting Strategy and Model Validation](https://github.com/Scibrokes/Betting-Strategy-and-Model-Validation/blob/master/Betting%20Strategy%20and%20Model%20Validation.Rmd). The purpose of writing the functions just would like easier future scrap teams name for further calculation to reduce my workload.
  
  Where the subject/topic is that the last course [Data Science Capstone](https://www.coursera.org/course/dsscapstone) on Coursera (JHU Johns Hopkins University) which I have failed few times and will retake on this coming October-2015 (Next month).
  
  Note that the `echo = FALSE` and `include=FALSE` parameters were added to the code chunks below to prevent printing of the R code that generated the plots/tables. However you can feel free to see the source code via [Natural Language Analysis.Rmd](https://github.com/Scibrokes/Betting-Strategy-and-Model-Validation/Natural Language Analysis.Rmd).



## 1. Setup Options, Loading Required Libraries and Preparing Environment

  Setup `knitr` options and loading the required libraries.

```{r libs, message=FALSE, warning=FALSE, cache=TRUE, include=FALSE}
## Loading the packages and setting adjustment
suppressMessages(source('function/libs.R'))
```



## 2. Read and Process the Dataset

  Read the dataset of World Wide soccer matches from year 2011 until 2015 from a British betting consultancy named firm A.

```{r read-datasetA, echo=FALSE, results='asis'}
## Read the datasets
## Refer to **Testing efficiency of coding.Rmd** at chunk `get-data-summary-table-2.1`
years <- seq(2011,2015)
mbase <- readfirmDatasets(years=years)
dateID <- sort(unique(as.Date(mbase$datasets$Date)))
```

*table 2.1* `r paste(unlist(strsplit(as.character(dim(mbase$datasets)), ' ')), collapse=' x ')`

  Due to the dataset very big `r paste(unlist(strsplit(as.character(dim(mbase$datasets)), ' ')), collapse=' x ')` caused the webpage keep loading and unable open. Here I just only subset few rows from the data frame.

  Read the dataset of World Wide soccer matches scrapped from year 2011 until 2015 from [spbo livescore website](http://www.spbo.com/eend0.htm).

```{r read-datasetB, echo=FALSE, results='asis'}
## Load the scraped spbo livescore datasets.
spboData <- readSPBO(dateID=dateID, parallel=TRUE)$data
spboData
```


